### 2019-02-27 Sections/economics_of_the_quantum_internet.tex
Minor economics, ZH corrections

Let $L(t)$ be the dollar-value of utilising the network's computing resources for a single unit of time. This is obtained as the return made on the value of the network per FLOP,
\begin{postulate}[Objective value of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation for a single unit of time at time $t$, per FLOP is,
\begin{align}\index{Cost of computation}
	L(t) &= \frac{e^{\gamma_\mathrm{ror}} V(t)}{P(t)} \nonumber\\
	&= \frac{e^{\gamma_\mathrm{ror}} C_0{\gamma_C}^{-t}}{\chi_\mathrm{sc}(N_0 {\gamma_N}^t)}.
\end{align}
\end{postulate}
which implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation per FLOP is,
\begin{align}
L(0) = \frac{e^{\gamma_\mathrm{ror}}C_0}{\chi_\mathrm{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the value of computations simply approximates the return on initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

Elements associated with \textsc{License} strategies are transformed as,
\begin{align}
\begin{pmatrix}
   f^{(X)}_\mathrm{sc}(n_X) \\
   f^{(Y)}_\mathrm{sc}(n_Y)
\end{pmatrix} \underset{\textsc{License}}{\longrightarrow} \begin{pmatrix}
   (1-r) \cdot f^{(X)}_\mathrm{sc}(n_X) \\
   f^{(Y)}_\mathrm{sc}(n_Y) + r \cdot f^{(Y)}_\mathrm{sc}(n_X)
\end{pmatrix},
\end{align}
where \mbox{$0\leq r\leq 1$} denotes the proportion of $X$'s compute-time licensed to $Y$. We have here implicitly assumed that $Y$'s compute-time is fully exploited by $Y$ alone, and none is licensed in the reverse direction\footnote{It would be a fruitless exercise for both $X$ and $Y$ to simultaneously license the same commodity to one another in both directions. Indeed, in a more realistic setting, in which transaction and communication costs are accommodated for, this would be inefficient and positively counterproductive.}.

This is easily logically generalised to an arbitrary multi-player setting, in which case the transformation becomes,
\begin{align}
	f_\mathrm{sc}^{(i)}(n_i) \underset{\textsc{License}}{\longrightarrow} \sum_{j=1}^N r_{j\to i} f_\mathrm{sc}^{(i)}(n_j),
\end{align}
where there are $N$ players, all engaging with one another using licensing only. Here, $r_{i\to j}$ denotes the proportion of $i$'s compute-time licensed to $j$, which are normalised (assuming no wasted clock-cycles) for all users such that,
\begin{align}
\sum_{j=1}^N r_{i\to j} = 1\,\,\forall\,i.	
\end{align}
Note that when \mbox{$r_{i\to j}=\delta_{i,j}$} (i.e \mbox{$r=I_N$} is the \mbox{$N\times N$} identity matrix, and there is no inter-player licensing) the \textsc{License} strategy simply reduces back to the \textsc{Isolation} strategy.

@@

Elements associated with \textsc{Unify} strategies will undergo the quantum utility payoff enhancement,
\begin{align}\label{eq:util_payoff_enh_1}
(f^{(X)}_\mathrm{sc}(n_X),f^{(Y)}_\mathrm{sc}(n_Y)) \underset{\textsc{Unify}}{\longrightarrow} (c_X,c_Y),
\end{align}
where,
\begin{align}\label{eq:util_payoff_enh_2}
c_X &= n_X \cdot \chi^{(X)}_\mathrm{sc}(n_X+n_Y),\nonumber\\
c_Y &= n_Y \cdot \chi^{(Y)}_\mathrm{sc}(n_X+n_Y),
\end{align}
from the definition for time-shared compute power given in Def.~\ref{def:time_share_comp_power}.

>>>>

Let $L(t)$ be the dollar-value of utilising the network's computing resources for a single unit of time. This is obtained as the return made on the value of the network per FLOP,
\begin{postulate}[Objective value of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation for a single unit of time at time $t$, per FLOP is,
\begin{align}\index{Cost of computation}
	L(t) &= \frac{e^{\gamma_\mathrm{ror}t} V(t)}{P(t)} \nonumber\\
	&= \frac{e^{\gamma_\mathrm{ror}t} C_0{\gamma_C}^{-t}}{\chi_\mathrm{sc}(N_0 {\gamma_N}^t)}.
\end{align}
\end{postulate}
which implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation per FLOP is,
\begin{align}
L(0) = \frac{C_0}{\chi_\mathrm{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the value of computations simply approximates the return on initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

Elements associated with \textsc{License} strategies are transformed as,
\begin{widetext}
\begin{align}
\begin{pmatrix}
   f^{(X)}_\mathrm{sc}(n_X) \\
   f^{(Y)}_\mathrm{sc}(n_Y)
\end{pmatrix} \underset{\textsc{License}}{\longrightarrow} \begin{pmatrix}
   r_{X\to X} \cdot f^{(X)}_\mathrm{sc}(n_X) + r_{Y\to X} \cdot f^{(X)}_\mathrm{sc}(n_Y) \\
   r_{Y\to Y} \cdot f^{(Y)}_\mathrm{sc}(n_Y) + r_{X\to Y} \cdot f^{(Y)}_\mathrm{sc}(n_X)
\end{pmatrix},
\end{align}
\end{widetext}
where \mbox{$0\leq r_{i\to j}\leq 1$} denotes the proportion of $i$'s compute-time licensed to $j$.

This is easily logically generalised to an arbitrary multi-player setting, in which case the transformation becomes,
\begin{align}
	f_\mathrm{sc}^{(i)}(n_i) \underset{\textsc{License}}{\longrightarrow} \sum_{j=1}^N r_{j\to i} f_\mathrm{sc}^{(i)}(n_j),
\end{align}
where there are $N$ players, all engaging with one another using licensing only. Here, $r_{i\to j}$ denotes the proportion of $i$'s compute-time licensed to $j$, which are normalised for all users such that,
\begin{align}
\sum_{j=1}^N r_{i\to j} \leq 1\,\,\forall\,i.	\
\end{align}

With equality, this normalisation implies perfect licensing efficiency (i.e no overheads) and no wasted clock-cycles (full utilisation). Inequality implies either inefficiency or under-utilisation. Since under this strategy net computational power is conserved (at best), it might appear mindless to employ it at all, given that there is no net gain. Whilst this is true, there may be ulterior motives for employing it. For example, it might be employed for the purposes of load balancing\index{Load balancing} across a distributed architecture, or implementing arbitrage\index{Arbitrage} between inconsistent market pricing of computational power between nodes.

Note that when \mbox{$r_{i\to j}=\delta_{i,j}$} (i.e \mbox{$r=I_N$} is the \mbox{$N\times N$} identity matrix, and there is no inter-player licensing) the \textsc{License} strategy simply reduces back to the \textsc{Isolation} strategy.

@@

Elements associated with \textsc{Unify} strategies will undergo the quantum utility payoff enhancement,
\begin{align}\label{eq:util_payoff_enh_1}
\begin{pmatrix}
	f^{(X)}_\mathrm{sc}(n_X)\\
	f^{(Y)}_\mathrm{sc}(n_Y)
\end{pmatrix}
 \underset{\textsc{Unify}}{\longrightarrow} \begin{pmatrix}
 	n_X \cdot \chi^{(X)}_\mathrm{sc}(n_X+n_Y)\\
 	n_Y \cdot \chi^{(Y)}_\mathrm{sc}(n_X+n_Y)
 \end{pmatrix},
\end{align}
from the definition for time-shared compute power given in Def.~\ref{def:time_share_comp_power}.
